Datasheet for 'Top 10000 Ranked Anime on MyAnimeList

### 2024-04-19 other/datasheet/datasheet.qmd
Removed extraneous section and fixed date for datasheet

---
title: "Datasheet for 'Top 10000 Ranked Anime on MyAnimeList'"
author: Allen Uy
thanks: "Code and data are available at: https://github.com/varygx/AnimeAnalysis"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Datasheet for 'Top 10000 Ranked Anime on MyAnimeList'"
author: Allen Uy
thanks: "Code and data are available at: https://github.com/varygx/AnimeAnalysis"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---
